---
title: "Vis_I"
output: github_document
---

```{r setup}
library(tidyverse)
library(ggridges)
library(hexbin)
```

## Load the weather data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())


weather_df
```


## Scatterplots!!

Create my first scatterplot ever!

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()
```

New approach, same plot!

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y =tmax)) +
  geom_point()
```

Save and edit a plot object!

```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```

Advanced scatterplot

Start with the same one and make it fancy

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y =tmax, color = name)) +
  geom_point() +
  geom_smooth(se = F)

```

`aes` placement?

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y =tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth()
```

Let's facet the same thing! .denote nothing stands for rows(try name ~ .)
geom_pint alpha controls the transparency (values or variable less transparency for greater value) try: alpha = tmin in ggplot
can use size for both geom_point/geom_smooth

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y =tmax, color = name)) +
  geom_point(alpha = .2, size = .3) +
  geom_smooth(se = F) +
  facet_grid(. ~ name)
```

Let's combine elements and try a new plot!

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = .5) +
  geom_smooth(se = F) +
  facet_grid(. ~ name)
```

## Some small notes

how many geoms have to exist?

you can have whatever geom you want.

```{r not recommended through}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_smooth(se = F)
```

You can use a neat geom! (require hexbin)

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex()

weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_bin2d()

weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_density2d() +
  geom_point(alpha = .2)
```

## Univerate plots

Histogram are really great!

```{r}
weather_df %>% 
  ggplot(aes(x = tmin)) +
  geom_histogram()
```

Can we add color?

```{r messy for multiple variables}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram(position = "dodge")
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram() +
  facet_grid(. ~ name)
```

Let's try a new geometry! adjust allow more individuals

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = .3, adjust = .5)
```

What about boxplot?

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmax)) +
  geom_boxplot()
```

Trendy plot

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin(alpha = .5) +
  stat_summary(fun = "median")
```

Ridge plots = the most popular plot of 2017

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = name)) +
  geom_density_ridges()
```

## Save and embed

Let's save a scatterplot!

```{r}
weather_plot =   
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5)

ggsave("./results/weather_plot.pdf", width = 8, height = 5)
```

What about embed?

```{r,fig.width=6, fig.height=3}
weather_plot
```

Embed at different size

```{rfig.width=12, fig.height=6}
weather_df
```

